Towards a Pandemic-Scale Ancestral Recombination Graph of SARS-CoV-2

### 2023-04-27 paper.tex

The \texttt{tskit} library~\citep{Tskit2023-tskit} is a liberally
licensed open source toolkit that provides a comprehensive suite
of tools for working with ARGs. Based on core functionality written
in C, it provides interfaces in C, Python and Rust. The Python interface
is based on NumPy~\citep{Harris2020-array}, and provides a convenient
platform for interactive analysis of large-scale data using, for
example, Jupyter notebooks~\citep{Kluyver2016-jupyter} and taking
advantage of the analysis tools in the burgeoning PyData ecosystem.
Tskit is mature software, widely used in population genetics, and
has been incorporated into several downstream
% TODO Add more - geonomics?
applications~\citep[e.g.][]{Speidel2019-yh,Haller2019-slim}

>>>>

The \texttt{tskit} library~\citep{Tskit2023-tskit} is a liberally
licensed open source toolkit that provides a comprehensive suite
of tools for working with ARGs. Based on core functionality written
in C, it provides interfaces in C, Python and Rust. The Python interface
is based on NumPy~\citep{Harris2020-array}, and provides a convenient
platform for interactive analysis of large-scale data using, for
example, Jupyter notebooks~\citep{Kluyver2016-jupyter} and taking
advantage of the analysis tools in the burgeoning PyData ecosystem.
Tskit is mature software, widely used in population genetics, and
has been incorporated into several downstream
applications~\citep[e.g.][]{Haller2019-slim,Speidel2019-yh,
Terasaki2021-geonomics,
Fan2022-genealogical,Korfmann2022-weak,
Mahmoudi2022-bayesian,Petr2022-slendr,Rasmussen2022-espalier}.
